---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
# README.Rmd is processed by the developer of the package 
# to create a README.md or README.html for the user of the package.
# The README should be processed as last step in the development process.
# This means that we should load here the latest version of the package.
# So that is what we will do below.
# 
# Also when we are developing the package and 
# in parallel writing the README, we want to use for the
# README the latest version of the package.
# 
# Load the latest version of the package that is under development.
if (requireNamespace("devtools", quietly = TRUE) && 
    file.exists("evalstratified.Rproj")) {
  devtools::load_all(".")
} else {
  # Error! Break off knitting process.
    stop("README evalstratified: no evalstratified.Rproj in current directory.")
}

# Set global knitr options for all subsequent chunks
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  
  # Route messages, warnings and errors to the R console, i.e. the developer.
  # Not to the resulting document, i.e. the reader.
  message = FALSE, 
  warning = FALSE, 
  error = FALSE
)
```

# evalstratified

<!-- badges: start -->
[![R-CMD-check](https://github.com/cfjdoedens/evalstratified/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/cfjdoedens/evalstratified/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of evalstratified is to make an estimate of the 
error fraction of a set of monetary files.
This based on a global level of certainty, a level of certainty per file,
and on error fractions
found in sampled items of each of these
files.

## Installation

You can install the development version of evalstratified from
[GitHub](https://github.com/) with:

```{r install, eval = FALSE, echo=TRUE}
  if (!requireNamespace("devtools", quietly = TRUE)) {
    install.packages("devtools")
  }
  devtools::install_github("cfjdoedens/evalstratified")
```

## Example

Steekproef1 is gebaseerd op een zekerheid van 95% omdat
ihr, ibr en car alledrie op hoog (H) staan.

De materialiteit is 2%.
Het betreft 100 miljoen euro.

Voor steekproef1 trekken we 148 posten, waarbij 1 fout blijkt.
Steekproef2 is gebaseerd op een zekerheid van 64% omdat
ihr en ibr allebei op laag staan en alleen car op hoog.
Het betreft ook 100 miljoen euro en een materialiteit van ook 2%.
Voor steekproef2 trekken we 50 posten waarvan er 0 fout blijken. 

```{r example}
library(evalstratified)

  example <- tribble(
      ~ naam,
      ~ w,
      ~ n,
      ~ k,
      ~ ihr,
      ~ ibr,
      ~ car,
      ~ materialiteit,
      "populatie1",
      100000000,
      148,
      1,
      'H',
      'H',
      'H',
      0.02,
      "populatie2",
      100000000,
      50,
      0,
      'L',
      'L',
      'H',
      0.02
    )
    r <- eval_stratified(steekproeven = example, zekerheid = 0.95)
    r

```

